\documentclass[11pt]{report}
\usepackage{standalone}
\graphicspath{ {images/} }
\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}
\usepackage{natbib}
\usepackage{bibentry}
\bibliographystyle{agsm}
\usepackage{etoolbox}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.25em}
\usepackage[raggedright]{titlesec}
\usepackage{hyperref}
\usepackage{capt-of}
\patchcmd{\bibliography}{\section*}{\section}{}{}
\titlespacing*{\chapter}{0pt}{-40pt}{10pt}
\titleformat{\chapter}[block]{\normalfont\huge\bfseries}{\thechapter}{15pt}{}
\usepackage{rotating}
\usepackage[titletoc]{appendix}
\usepackage{pgfgantt}
\usepackage{graphicx, rotating, caption, lscape, threeparttable}% \usepackage{amsmath}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{geometry}
\usepackage{listings}
\usepackage[T1]{fontenc}
\usepackage[bottom]{footmisc}


\begin{document}
\section*{Appendix A. System Classified Tweets}

\subsection*{Correctly Classified Brexit Tweets}

\subsubsection*{Tweets Classified Leave}
-- ``Out of sheer envy the EU mandated that we pay \pounds1.7bn worth of contributions in 2014 wishing to free-load on our economic success. After all we procure goods from them. Now they set a figure within the region of \pounds40bn. What justifies this farcical calculation \#Brexit''

-- ``Get over it, we're on our way out \#Brexit''

\subsubsection*{Tweets Classified Remain}
-- ``How much of a hit to the economy would you take to prevent foreigners coming to the UK? \#Remain''

--``The economic and political cost of UK austerity \#Brexit \#FBPE \#StopBrexitSaveBritain \#FinalSay http://bit.ly/2FQhHwo''
\subsection*{Incorrectly Classified Brexit Tweets}

\subsubsection*{Tweets Classified Leave}
--``Yeah, \#Brexit .....because it's so much easier to negotiate trade deals with big powerful countries when you're not part of a powerhouse trading block! Oh, wait....''

\subsubsection*{Tweets Classified Remain}
--``Brexit is 9527 hours away. \#brexit''

-- ``Die hard \#Brexit''

\subsection*{Correctly Classified Sentiment Tweets}

\subsubsection*{Tweets Classified Positive}
-- ``This is an interesting point. First of all, we need another election, and soon. Then maybe we can get to where \#Brexit can be re-considered.''

-- ``Looking forward to see what last-minute deal the UK will offer the Republic not to veto its \#Brexit negotiations with the EU. Any offer they make will be of great interest, especially in the instance Scotland revisits the question of whether it wants to be independent again.''

\subsubsection*{Tweets Classified Negative}
-- ``Angela Merkel's open-door policy CAUSED the migrant crisis led to \#brexit in \#eu , furious George Soros blasts http://shr.gs/suCTcuW''

-- ``It has been said that you should, "Never trust a Tory." So why should it be any different during the Brexit negotiations? \#BrexitMeansBrexit \#BrexitPerversion \#Brexit \#MayMustGo https://youtu.be/CZ4lhmARnCc''

\subsection*{Incorrectly Classified Sentiment Tweets}

\subsubsection*{Tweets Classified Positive}
-- ``Stop being so negative. Get behind \#brexit and be positive. You're ignoring the will of the people. They elected May and Tories. You're an A Grade Bremoaner''

-- ``No. That's precisely the point. That's the deception here. It's totally and utterly clear that \#Corbyn is a \#Brexiter and that he and @UK Labour WILL deliver \#Brexit come what may. He has said so - repeatedly. There will be no u-turn. That's why it's \#Remain OR \#Labour''

\subsubsection*{Tweets Classified Negative}
-- ``RT @conorwells0: A Huge Thank you to everyone for their superb and supportive comments since I switched from Leave to Remain, we must fight...''

--``@David\textunderscore Cameron Put this poster in your window and send local politicians a message. \#Brexit https://t.co/6cxCsZKhSv''


\subsection*{Off Discussion Topic Tweets}
-- ``How the NRA uses an app to organize opposition to gun control via @Salon \#Brexit \#StopBrexit https://buff.ly/2CjFXs8''

-- ``Greece needs capital, ingenious Irish biscuits and mince pies. \#ExportOpps \#TakeBackControl''

--`\#ButHerEmails -> WAR \#RussiaGate \#Assange \#Putin \#InfoWars \#Trump \#Breitbart \#AlexJones \#Murdoch \#Mercer \#Brexit \#Milo \#Forage Alt-right https:// twitter.com/angryblacklady /status/895279622983516160 …''

\end{document}
